\documentclass[12pt]{report}
% \documentclass[12pt,letterpaper]{article}
\usepackage{preamble}

% \newcommand\course{}
% \newcommand\hwnumber{}
% \newcommand\userID{Jason Yao}
% \newcommand\collaborator{V. Houh, G. Summermatter}
\newcommand{\sectionbreak}{\clearpage}
\newcommand*\mean[1]{\overline{#1}}
\newcommand\np{\vspace{0.5cm}\\} % as in "next point"
\newcommand\nl{\vspace{5mm}\hrule\vspace{5mm}\noindent} % as in "new line"

\title{The Missing Steps in Griffiths}
\author{Jason Yao}
\date{June 9, 2021}


\graphicspath{{Images/}}
\setcounter{tocdepth}{3}

\begin{document}

\maketitle

\numberwithin{equation}{section}

\tableofcontents

\clearpage
\begin{multicols}{2}
In this document, I attempt to include all the explanations to things that confused the heck out of me during my first read through (and the second, third, you get the idea). Usually, these are derivations that have around 10,000 missing steps in between --- the kind of derivations that Griffiths seems to enjoy making. Occasionally, I will include alternative ways to interpret/derive results. These mainly come from Brant Carlson's YouTube Channel. Finally, please understand that this document is by no means intended to be a self-contained piece --- for that we have these things that are commonly known to scholars as ``books'' and to publishers as ``books (799 USD)'' ---instead, this document is created to assist you in reading the textbook. When referring to previous equations, instead of something like ``see Eq. (420)'' (and then you have to scroll through two-hundred pages on a computer), I will try as much as possible to utilize mouse-over tooltips, like \tooltip{so}{
\parbox{10cm}
{ The end-all-be-all equation: 
\begin{equation*}
    i\hbar\pdv{\Psi}{t}=-\frac{\hbar^2}{2m}\pdv[2]{\Psi}{x}+V\Psi
\end{equation*}
}}. 
The tooltip feature, however, is pretty much only supported by Adobe software, so you will most likely need to read this using their (free) Acrobat Reader. (If you truly are a rebel who hates being told what to do, feel free to use Preview on you Mac, and good luck with that.) Alternatively, you can simply go print this out using Chem Department's printer, and on your way back to the Physics Lounge, see if you can \st{steal} borrow some staplers and tapes, among other things, for the greater good of mankind.
\end{multicols}


\input{chapter01}
\input{chapter02}




\end{document}

